### 2016-05-18 writing/latex/confut.tex
Anders chap3/4

If we are inside \(\av{\perm{2,3,1}}\) then any points in the region corresponding
to the box \(b_1\) must be to the right of the points in the region corresponding to
box \(b_2\), and must also form a decreasing subsequence by \LemmaRef{lem:incdec}.
Furthermore, the points in the regions corresponding to \(b_2\) and
\(b_3\) must form an avoider of \(\perm{2,3,1}\) with the indicated point.
Therefore the containers of \(p\) in \(\av{\perm{2,3,1}}\) have generating function
\(\lastvar(x) = \frac{x(C(x)-1)}{1-x}\).
Now, if we are \(\av{\perm{3,2,1}}\) then any points in the region corresponding
to the box \(b_1\) must be to the left of the points in the region corresponding to
box \(b_2\), and must also form a increasing subsequence by \LemmaRef{lem:incdec}.
Furthermore, the points in the regions corresponding to \(b_2\) and
\(b_3\) must form an avoider of \(\perm{3,2,1}\) with the indicated point.
Hence, the containers of \(p\) in \(\av{\perm{3,2,1}}\) have generating function
\(\var(x) = \frac{x(C(x)-1)}{1-x}\) and both of these classes have the same
enumeration.

>>>>

If we are inside \(\av{\perm{2,3,1}}\) then any points in the region corresponding
to the box \(b_1\) must be to the right of the points in the region corresponding to
box \(b_2\), and must also form a decreasing subsequence by \LemmaRef{lem:incdec}.
Furthermore, the points in the regions corresponding to \(b_2\) and
\(b_3\) must form an avoider of \(\perm{2,3,1}\) with the indicated point.
Therefore the containers of \(p\) in \(\av{\perm{2,3,1}}\) have generating function
\(\lastvar(x) = x(C(x)-1)/(1-x)\).
Now, if we are in \(\av{\perm{3,2,1}}\) then any points in the region corresponding
to the box \(b_1\) must be to the left of the points in the region corresponding to
box \(b_2\), and must also form a increasing subsequence by \LemmaRef{lem:incdec}.
Furthermore, the points in the regions corresponding to \(b_2\) and
\(b_3\) must form an avoider of \(\perm{3,2,1}\) with the indicated point.
Hence, the containers of \(p\) in \(\av{\perm{3,2,1}}\) have generating function
\(\var(x) = x(C(x)-1)/(1-x)\) and both of these classes have the same
enumeration.

### 2016-05-18 writing/latex/introduction.tex
Introduction for presentation
Anders chap3/4

\chapter{Introduction\label{cha:introduction}}
\section{What is a Permutation?}
In \emph{The Art of Computer Programming} \cite[p.~45]{Knuth:1997:ACP:260999} Knuth states,
\enquote{A \emph{permutation of \(n\) objects} is an arrangement of \(n\) distinct
objects in a row}.
When considering permutations we can consider them as
occurring on the set \(\nrange{n} = \setrange{1}{n}\), therefore a permutation
is a \emph{bijection} \(\pi:\nrange{n} \mapsto \nrange{n}\). A
permutation \(\pi\) can be written in two-line notation
\begin{equation*}
\pi = \twoline{1,2,\dotso,n}{\pi(1),\pi(2),\dotso,\pi(n)}
\end{equation*}
However,
This
% most frequent
notation
% used in computer science
is called
\emph{one-line notation}.
% in this form we drop the top line of the two line
% notation and are left with the following.
In this form we write the entries of the permutation in order, and get
\begin{equation*}
\pi = \perm{\pi(1),\pi(2),\dotso,\pi(n)}
\end{equation*}

@@

\section{Mesh Patterns}
Mesh patterns were introduced by \textcite{journals/combinatorics/BrandenC11} to
capture explicit expansions for certain permutation statistics. They are a
natural extension of classical permutation patterns.
A \emph{mesh pattern} is a pair
\begin{equation*}
    p = (\pi,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq
    [0,k]\times [0,k].
\end{equation*}

@@

We define containment (denoted \(p\preceq \pi\)), and avoidance, of the pattern \(p\) in the permutation
\(\tau\) on mesh patterns analogously to classical containment, and avoidance,
of \(\pi\) in \(\tau\) with the additional restrictions on the relative
position of the occurrence of \(\pi\) in \(\tau\). These restrictions say that
no elements of \(\tau\) are allowed in the regions of the plot corresponding
to shaded boxes in the mesh. Formally defined by \textcite{journals/combinatorics/BrandenC11},
an \emph{occurrence} of \(p\) in \(\tau\) is a subset \(\omega\) of the plot of
\(\tau, G(\tau) = \{(i,\tau(i)\mid i\in[1,n]\}\) such that there are order-preserving
injections \(\alpha,\beta:[1,k]\mapsto[1,n]\) satisfying the following two conditions.

@@

In the past people have studied different classes
of permutations that can be described by mesh patterns. \textcite{babstein2000}
considered \emph{vincular} patterns (also known as \emph{generalised} or \emph{dashed} patterns),
those where two adjacent entries in the pattern must be adjacent in the permutation,
\ie \(R\) is a union of vertical strips.
\textcite{MR2652101} look at classes of pattern where both columns and rows
can be shaded, these are called \emph{bivincular} patterns.
\emph{Bruhat-restricted} patterns were studied by \textcite{MR2264071} in order
to establish necessary conditions for a Schubert variety to be Gorenstein.
Mesh patterns also encompass a subset of \emph{barred} patterns introduced by
\textcite{MR2716312}, those with only one barred letter.

>>>>

\chapter{Introduction\label{cha:introduction}}
\section{What is a Permutation?}
In \emph{The Art of Computer Programming} \cite[p.~45]{Knuth:1997:ACP:260999} Knuth states,
\enquote{A \emph{permutation of \(n\) objects} is an arrangement of \(n\) distinct
objects in a row}.
When considering permutations we can consider them as
occurring on the set \(\nrange{n} = \setrange{1}{n}\), therefore a permutation
is a \emph{bijection} \(\pi:\nrange{n} \mapsto \nrange{n}\). %A
% permutation \(\pi\) can be written in two-line notation
% \begin{equation*}
% \pi = \twoline{1,2,\dotso,n}{\pi(1),\pi(2),\dotso,\pi(n)}
% \end{equation*}
% However,
This
% most frequent
notation
% used in computer science
is called
\emph{one-line notation}.
% in this form we drop the top line of the two line
% notation and are left with the following.
In this form we write the entries of the permutation in order, and get
\begin{equation*}
\pi = \perm{\pi(1),\pi(2),\dotso,\pi(n)}
\end{equation*}

@@

\section{Mesh Patterns}
Mesh patterns were introduced by \textcite{journals/combinatorics/BrandenC11} to
capture explicit expansions for certain permutation statistics. They are a
natural extension of classical permutation patterns.
A \emph{mesh pattern} is a pair
\begin{equation*}
    p = (\tau,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq
    [0,k]\times [0,k].
\end{equation*}

@@

Looking at the classical pattern \(\perm{2,3,1}\), any occurrences can be arbitrarily
placed. However it may be interesting to consider occurrences where the elements
corresponding to the \(2\) and \(3\) are adjacent in the permutation. In the past
these sort of questions have lead to a variety of definitions.  \textcite{babstein2000}
considered \emph{vincular} patterns (also known as \emph{generalised} or \emph{dashed} patterns),
those where two adjacent entries in the pattern must be adjacent in the permutation,
\ie \(R\) is a union of vertical strips.
\textcite{MR2652101} look at classes of pattern where both columns and rows
can be shaded, these are called \emph{bivincular} patterns.
\emph{Bruhat-restricted} patterns were studied by \textcite{MR2264071} in order
to establish necessary conditions for a Schubert variety to be Gorenstein.
Mesh patterns also encompass a subset of \emph{barred} patterns introduced by
\textcite{MR2716312}, those with only one barred letter.
All of these definitions subsumed under the definition of mesh patterns.
The example of an occurrence of \(\perm{2,3,1}\) with adjacent elements \(31\)
can be represented as a mesh pattern by
\begin{equation*}
  \pattern{}{2,3,1}{1/0,1/1,1/2}
\end{equation*}

We define containment (denoted \(p\preceq \pi\)), and avoidance, of the pattern \(p\) in the permutation
\(\tau\) on mesh patterns analogously to classical containment, and avoidance,
of \(\pi\) in \(\tau\) with the additional restrictions on the relative
position of the occurrence of \(\pi\) in \(\tau\). These restrictions say that
no elements of \(\tau\) are allowed in the regions of the plot corresponding
to shaded boxes in the mesh.

Formally defined by \textcite{journals/combinatorics/BrandenC11},
an \emph{occurrence} of \(p\) in \(\tau\) is a subset \(\omega\) of the plot of
\(\tau, G(\tau) = \{(i,\tau(i)\mid i\in[1,n]\}\) such that there are order-preserving
injections \(\alpha,\beta:[1,k]\mapsto[1,n]\) satisfying the following two conditions.

@@

% In the past people have studied different classes
% of permutations that can be described by mesh patterns.
% \textcite{babstein2000}
% considered \emph{vincular} patterns (also known as \emph{generalised} or \emph{dashed} patterns),
% those where two adjacent entries in the pattern must be adjacent in the permutation,
% \ie \(R\) is a union of vertical strips.
% \textcite{MR2652101} look at classes of pattern where both columns and rows
% can be shaded, these are called \emph{bivincular} patterns.
% \emph{Bruhat-restricted} patterns were studied by \textcite{MR2264071} in order
% to establish necessary conditions for a Schubert variety to be Gorenstein.
% Mesh patterns also encompass a subset of \emph{barred} patterns introduced by
% \textcite{MR2716312}, those with only one barred letter.
